Manuscript

### 2015-07-15 inst/wtc-finland/manuscript2.Rmd
...

```{r initialize}
#library(devtools)
#install_github("statguy/WTC")
#install_github("ropengov/gisfin")
#install_github("statguy/SpaceTimeModels")
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(WTC)
source("~/git/Winter-Track-Counts/setup/WTC-Boot.R")
library(ggplot2)
library(scales)
library(grid)
library(plyr)
library(gridExtra)
library(SpaceTimeModels)

@@

```{r figure-convolution-example}
# Habitat
r <- raster::crop(study$studyArea$habitat, extent(3400000, 3410000, 7000000, 7010000))
#plot(r)
forest <- raster::calc(r, function(x) if (is.na(x) || x %in% c(0,45:255)) NA else x %in% 18:35)
#plot(forest)
coords <- raster::xyFromCell(r, cell=1:ncell(r))
x <- SpaceTimeModels::smoothContinuousSubsets(r=forest, coords=coords, kernel=SpaceTimeModels::ExponentialKernel$new(), scales=c(125, 1000), .parallel=T)
#plot(flip(rasterFromXYZ(x[,c("x","y","value")]), direction="y"), asp=1)
fileName <- study$context$getFileName(dir=study$context$processedDataDirectory, name="figure-b-1", region=study$studyArea$region)
save(x, file=fileName)
load(fileName)

@@

library(gisfin)
request <- gisfin::GeoStatFiWFSRequest$new()$getPopulation("vaestoruutu:vaki2005_1km")
client <- gisfin::GeoStatFiWFSClient$new(request)
population <- client$getLayer("vaestoruutu:vaki2005_1km")
population <- raster::stack(sp::SpatialPixelsDataFrame(coordinates(population), population@data, proj4string=population@proj4string))
population <- projectRaster(population$vaesto, crs="+init=epsg:2393")
r <- raster::crop(population$vaesto, extent(3400000, 3410000, 7000000, 7010000) * 10)
r[is.na(r)] <- 0
r1 <- as.data.frame(rasterToPoints(r))
colnames(r1) <- c("x","y","value")
coords <- raster::xyFromCell(r, cell=1:ncell(r))
x <- SpaceTimeModels::smoothContinuousSubsets(r=r, coords=coords, kernel=SpaceTimeModels::ExponentialKernel$new(), scales=c(2000), .parallel=T)

@@

# Elevation model data: http://www.eea.europa.eu/data-and-maps/data/digital-elevation-model-of-europe
elevation <- raster(file.path(context$rawDataDirectory, "elevation1x1_new.tif"))
r <- raster::crop(elevation, extent(elevation, 200, 1500, 2600, 3500))
raster::projection(r) <- "+proj=laea +lat_0=52 +lon_0=20 +x_0=5071000 +y_0=3210000 +a=6378137 +b=6378137 +units=m +no_defs"
elevation <- raster::projectRaster(r, crs="+init=epsg:2393")
r <- raster::crop(elevation, extent(3400000, 3410000, 7000000, 7010000) * 10)
s <- raster(extent(3355003, 3455003, 6955246, 7055246), 100, 100, crs="+proj=laea +lat_0=52 +lon_0=20 +x_0=5071000 +y_0=3210000 +a=6378137 +b=6378137 +units=m +no_defs")
r <- raster::resample(r, s) # Changing projection does not work good enough. Have to resample to fix.
r1 <- as.data.frame(rasterToPoints(r))
colnames(r1) <- c("x","y","value")
coords <- raster::xyFromCell(r, cell=1:ncell(r))
x <- SpaceTimeModels::smoothContinuousSubsets(r=r, coords=coords, kernel=SpaceTimeModels::ExponentialKernel$new(), scales=c(2000), .parallel=T)

>>>>

```{r initialize}
#library(devtools)
#install_github("statguy/WTC")
#install_github("ropengov/gisfin")
#install_github("statguy/Blur")
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(WTC)
source("~/git/Winter-Track-Counts/setup/WTC-Boot.R")
library(ggplot2)
library(scales)
library(grid)
library(plyr)
library(gridExtra)
library(Blur)

@@

```{r figure-convolution-example}
# Habitat
r <- raster::crop(study$studyArea$habitat, extent(3400000, 3410000, 7000000, 7010000))
#plot(r)
forest <- raster::calc(r, function(x) if (is.na(x) || x %in% c(0,45:255)) NA else x %in% 18:35)
#plot(forest)
coords <- raster::xyFromCell(r, cell=1:ncell(r))
x <- Blur::smoothContinuousSubsets(r=forest, coords=coords, kernel=Blur::ExponentialKernel$new(), scales=c(125, 1000), .parallel=T)
#plot(flip(rasterFromXYZ(x[,c("x","y","value")]), direction="y"), asp=1)
fileName <- study$context$getFileName(dir=study$context$processedDataDirectory, name="figure-b-1", region=study$studyArea$region)
save(x, file=fileName)
load(fileName)

@@

library(gisfin)
request <- gisfin::GeoStatFiWFSRequest$new()$getPopulation("vaestoruutu:vaki2005_1km")
client <- gisfin::GeoStatFiWFSClient$new(request)
population <- client$getLayer("vaestoruutu:vaki2005_1km")
population <- raster::stack(sp::SpatialPixelsDataFrame(coordinates(population), population@data, proj4string=population@proj4string))
population <- projectRaster(population$vaesto, crs="+init=epsg:2393")
r <- raster::crop(population$vaesto, extent(3400000, 3410000, 7000000, 7010000) * 10)
r[is.na(r)] <- 0
r1 <- as.data.frame(rasterToPoints(r))
colnames(r1) <- c("x","y","value")
coords <- raster::xyFromCell(r, cell=1:ncell(r))
x <- Blur::smoothContinuousSubsets(r=r, coords=coords, kernel=Blur::ExponentialKernel$new(), scales=c(2000), .parallel=T)

@@

# Elevation model data: http://www.eea.europa.eu/data-and-maps/data/digital-elevation-model-of-europe
elevation <- raster(file.path(context$rawDataDirectory, "elevation1x1_new.tif"))
r <- raster::crop(elevation, extent(elevation, 200, 1500, 2600, 3500))
raster::projection(r) <- "+proj=laea +lat_0=52 +lon_0=20 +x_0=5071000 +y_0=3210000 +a=6378137 +b=6378137 +units=m +no_defs"
elevation <- raster::projectRaster(r, crs="+init=epsg:2393")
r <- raster::crop(elevation, extent(3400000, 3410000, 7000000, 7010000) * 10)
s <- raster(extent(3355003, 3455003, 6955246, 7055246), 100, 100, crs="+proj=laea +lat_0=52 +lon_0=20 +x_0=5071000 +y_0=3210000 +a=6378137 +b=6378137 +units=m +no_defs")
r <- raster::resample(r, s) # Changing projection does not work good enough. Have to resample to fix.
r1 <- as.data.frame(rasterToPoints(r))
colnames(r1) <- c("x","y","value")
coords <- raster::xyFromCell(r, cell=1:ncell(r))
x <- Blur::smoothContinuousSubsets(r=r, coords=coords, kernel=Blur::ExponentialKernel$new(), scales=c(2000), .parallel=T)
